---
title       : "Covid - County Analysis"
subtitle    : "Regressions"
author      :  Victor Chernozhukov, Hiro Kasahara, Paul Schrimpf
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        code_folding: hide
        self_contained : true
        fig_width: 8
        fig_height: 6
---

 <!-- To create html files from this, in R enter  -->
 <!-- library(rmarkdown) -->
 <!-- rmarkdown::render("regressionsWithPlots.Rmd") -->
 <!-- To create tex files from this, in R enter ` -->
 <!-- library(rmarkdown) -->
 <!-- rmarkdown::render("regressionsWithPlots.Rmd", output_format=latex_fragment()) -->


 <!-- to create the gh-pages hosted website in R enter -->
 <!-- rmarkdown::render_site() -->

 <!-- Then in a shell  -->
 <!-- $ ghp-import -p -n -m "$(date)" _site -->


# Data Preparation
```{r setup, cache=FALSE, warning=FALSE, include=FALSE}
library(latex2exp)
library(ggplot2)
library(data.table)
library(ggthemes)

figtheme <- theme_pander() #+ theme(plot.title=element_text(face="plain"))
thm <-  theme(legend.text = element_text(size = 22),
              title = element_text(size=22, face='bold'),legend.position = c(0.23, 0.83),
              axis.text.x = element_text(size = 22, face='bold'),
              axis.text.y = element_text(size = 22, face='bold'),
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_rect(fill = "transparent",colour = NA),
              plot.background = element_rect(fill = "transparent",colour = NA))

figtheme <- figtheme + thm

colors <-  scale_color_gdocs
fills <- scale_fill_gdocs

rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
source(paste(rootdir,"R/countyData.R",sep="/"))
source(paste(rootdir,"R/varlabels.R", sep="/"))

cc <- countyData(FALSE)

dt <- cdcCaseData()
cols <-  c(names(dt)[grep("_yn", names(dt))],"current_status","race_ethnicity_combined","sex","age_group")
dt[,(cols):=lapply(.SD, as.factor),.SDcols=cols]

countyage <- dt[,list(cases=.N),
                by=list(cdc_case_earliest_dt, county_fips_code, age_group)]
countyage[order(county_fips_code, age_group, cdc_case_earliest_dt)]
setkey(countyage, cdc_case_earliest_dt)
countyage[, case_ma := frollmean(cases, 7), by=list(county_fips_code, age_group)]

cc[,weekcases:=frollsum(newcases, 7), by=fips]
cc[,weekcases_cdc:=frollsum(newcases_cdc, 7), by=fips]
```

# Comparing CDC and NYT Case Data

An important caveat in the age based data is that it comes from CDC
case reports. In this data, each case has a date reported to the CDC,
a symptom onset date, and a positive specimen date. However, the
symptom onset date and positive specimen date are missing for about
half of the 8.5 million cases. The report data is always included. We
use the CDC report date to compute total new cases by county, age
group, and day. This leads to some discrepencies between cumulative
case totals in the NYT data and those we compute from the CDC data.

```{r cumulative, cache=TRUE}
ggplot(cc, aes(x=cases,y=cases_cdc)) +
  geom_point() +
  xlab("Cumulative cases from NYT") +
  ylab("Cumulative cases calculated from CDC") +
  figtheme
```

The discrepencies look larger if we look at new cases each day.

```{r daily, cache=TRUE}
ggplot(cc, aes(x=newcases,y=newcases_cdc)) +
  geom_point() +
  xlab("New cases from NYT") +
  ylab("New cases from CDC") +
  figtheme
```

```{r weekly, cache=TRUE}
ggplot(cc, aes(x=weekcases,y=weekcases_cdc)) +
  geom_point() +
  xlab("Cases in past week from NYT") +
  ylab("Cases in past week from CDC") +
  figtheme
```

# Cases by Age Group in Select Counties

```{r countyage}
library(ggplot2)
library(tools)
sizes <- rep(0.2, length(unique(dt$age_group)))
sizes[1:3] <- 0.99
names(sizes) <- levels(dt$age_group)

dft <- data.table(cc)
dft$date <- as.IDate(dft$date)
setkey(dft,date)
dft[, sv_ma := frollmean(school_visits, 7), by=fips]
dft[, cv_ma := frollmean(college_visits, 7), by=fips]
dft[, bv_ma := frollmean(bar_visits, 7), by=fips]
dft[, gv_ma := frollmean(gym_visits, 7), by=fips]
dft[, rv_ma := frollmean(restaurant_visits, 7), by=fips]
dft[, wv_ma := frollmean(church_visits, 7), by=fips]
mcols <- c("fips","date","school_visits","college_visits","bar_visits",
           "gym_visits","restaurant_visits","church_visits",
           "sv_ma","cv_ma","bv_ma",
           "gv_ma","rv_ma","wv_ma",
           "county","state","newcases_cdc","newcases","weekcases","weekcases_cdc")
ctm <- merge(dft[,..mcols],countyage,
             by.x=c("fips","date"),
             by.y=c("county_fips_code","cdc_case_earliest_dt"),
             all=TRUE)
setkey(ctm, date)

lbls <- c("school","college","bar","gym","restaurant","church")
countyplot <- function(ct, st, fip=unique(ctm[county==ct & state==st]$fips),
                       daterange=c(as.Date("2020-07-01"),as.Date("2020-12-13"))
                       ) {
  tmp  <- melt(ctm[fips==fip],
               c("fips","age_group","date"),
               #names(ctm)[grep("_ma",names(ctm))])
               "case_ma")
  tmp <- tmp[!is.na(tmp$age_group)]
  tmp <- tmp[date>as.Date("2020-04-01")]
  #lbls  <-  c("cases","school visits","college vistis", "bar visits")
  #names(lbls)  <-  levels(tmp$variable)
  fig <- list()
  fig[[1]] <- ggplot(tmp, aes(x=date, y=value, colour=age_group, alpha=age_group)) +
    xlab("Date") +
    ylab("7 day moving average of cases") +
    xlim(daterange) +
    geom_line(size=1.5) +
    scale_alpha_manual(values=sizes) +
    figtheme +
    theme(legend.position = "none") +
    colors() + fills() +
    geom_label(aes(x=date, y=value, label=age_group,
                   colour=age_group),
               #colour="white",
               #alpha=0.5,
               data=tmp[date=="2020-11-15"],
               ) +
    ggtitle(sprintf("%s - %s",st,ct))
  vars <- c("sv_ma","cv_ma","bv_ma","gv_ma","rv_ma","wv_ma")
  tmp  <- ctm[fips==fip & date>=daterange[1]]
  for(i in 1:length(vars)) {
    fig[[i+1]] <- ggplot(tmp, aes_string(x="date",
                                         y=vars[i])) +
      xlab("Date") +
      ylab(sprintf("7 day moving average of %s visits",lbls[i])) +
      geom_line(size=1.5) +
      xlim(daterange) +
      figtheme +
      colors() +
      ggtitle(sprintf("%s visits in %s - %s county",toTitleCase(lbls[i]),st,ct))
  }
  fig[[i+1]] <- ggplot(dft[fips==fip], aes(x=date, y=weekcases/7, colour="NYT")) +
    geom_line(size=1.5) +
    geom_line(size=1.5,aes(y=weekcases_cdc/7, colour="CDC")) +
    ggtitle(sprintf("Comparison of cases in NYT and CDC data in %s - %s",st,ct)) +
    ylab("7 day moving average of new cases") +
    xlim(daterange) + figtheme + colors()
  return(fig)
}

c <- "Dane"
s <- "Wisconsin"

savecountyfigs <- function(figs,c,s, width=8,height=6) {
  pdf(sprintf("casesByAge%s%s.pdf",s,c), width=width,height=height)
  print(figs[[1]])
  dev.off()

  for (i in 1:length(lbls)) {
    pdf(sprintf("%s%s%s.pdf",lbls[i],s,c), width=width,height=height)
    print(figs[[i+1]])
    dev.off()
  }
}

figs <- countyplot(c,s)
wd <- getwd()
figuredir <- paste(rootdir,"tex/tables_and_figures/county",sep="/")
if (!dir.exists(figuredir)) dir.create(figuredir)
setwd(figuredir)
savecountyfigs(figs, c, s)
setwd(wd)

print(figs[[7]])
print(figs[[1]])
library(patchwork)
print(wrap_plots(figs[2:3], ncol=1))
print(wrap_plots(figs[4:6], ncol=1))
```

```{r counties}
# some counties with large universities
places <- list(c("Centre","Pennsylvania"),
               c("Pima", "Arizona"),
               c("Alachua","Florida"),
               c("Champaign","Illinois"),
               c("Allen","Indiana"),
               c("Story","Iowa"),
               c("Ingham","Michigan"),
               c("Lafayette","Mississippi"),
               c("Missoula","Montana"),
               c("Lane","Oregon"),
               c("Greenville","South Carolina"))

for (cs in places)  {
  c <- cs[1]
  s <- cs[2]
  cat(s,"\n")
  figs <- countyplot(c,s)
  print(figs[[7]])
  print(figs[[1]])

  print(wrap_plots(figs[2:3], ncol=1))
  print(wrap_plots(figs[4:6], ncol=1))
  setwd(figuredir)
  savecountyfigs(figs, c, s)
  setwd(wd)
}
```
