---
title       : "Covid - County Analysis"
subtitle    : "eventstudy"
author      :  Victor Chernozhukov, Hiro Kasahara, Paul Schrimpf
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        code_folding: hide
        self_contained : true
        fig_width: 8
        fig_height: 6
---

 <!-- To create html files from this, in R enter  -->
 <!-- library(rmarkdown) -->
 <!-- rmarkdown::render("regressionsWithPlots.Rmd") -->
 <!-- To create tex files from this, in R enter ` -->
 <!-- library(rmarkdown) -->
 <!-- rmarkdown::render("regressionsWithPlots.Rmd", output_format=latex_fragment()) -->


 <!-- to create the gh-pages hosted website in R enter -->
 <!-- rmarkdown::render_site() -->

 <!-- Then in a shell  -->
 <!-- $ ghp-import -p -n -m "$(date)" _site -->



# Data Preparation
```{r setup, cache=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)
library(ggthemes)
library(data.table)
<<<<<<< variant A
>>>>>>> variant B

library(lfe)
library(stargazer)
library(knitr)
library(plm)
library(latex2exp)
library(mvtnorm)
library(kableExtra)
library(readxl)
library(dplyr)
library(dotwhisker)
library(latex2exp)
library(parallel)
detectCores()

======= end
#library(devtools)
#devtools::install_github("bcallaway11/did")
library(did)

colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]

source(paste(rootdir,"R/countyData.R",sep="/"))
source(paste(rootdir,"R/varlabels.R", sep="/"))
source(paste(rootdir,"R/dataprep.R",sep="/"))
source(paste(rootdir,"R/utils.R", sep="/"))

library(tidyverse)
library(haven)

thm <-  theme(legend.text = element_text(size = 18), title =element_text(size=18, face='bold'),legend.position = c(0.23, 0.8),
              axis.text.x = element_text(size = 18), axis.text.y = element_text(size = 18),
       # panel.grid.major = element_blank(),
       # panel.grid.minor = element_blank(),
       # panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA))

```

```{r loaddata, warning = FALSE, cache=FALSE}
# if (TRUE) {
#   df <- countyData(redo=FALSE)
#   df <- dataprep(df)
#   save(df, file="tmp.Rdata")
# } else {
#   load("tmp.Rdata")
# }

df <- countyData(redo=FALSE)
df <- dataprep(df)


df <- subset(df, df$date>=as.Date("2020-02-01"))
startdate  <- "2020-04-01"
enddate  <- "2021-12-02"
sdf <- subset(df, df$date>=as.Date(startdate))
sdf <- subset(sdf, sdf$date<=as.Date(enddate))
sdf <- subset(sdf, sdf$fips!=0)
sdf$pgather <- sdf$pgather50

## replace start.full, start.hybrid, start.remote with NA based on the school opening status: pfull, phybrid, premote
sdf[which(pfull==1),c("start.Hybrid","start.Remote")] <- NA
sdf[which(phybrid==1),c("start.Full","start.Remote")] <- NA
sdf[which(premote==1),c("start.Hybrid","start.Full")] <- NA

## obtain schooling opening date
tdf <- sdf[,grep("start.",names(sdf)), with=FALSE]
sdf$start.first <- as.Date(apply(tdf, 1, function(x) min(x, na.rm=TRUE)))
sdf$event_week <- as.numeric(floor(difftime(sdf$date, sdf$start.first, units="weeks")))
rm(tdf)

## did packages wants numeric time and individual identifies
sdf$week <- as.numeric(floor(difftime(sdf$date,min(sdf$date), units="weeks")))
sdf$nfips <- as.numeric(sdf$fips)
sdf <- data.table(sdf, key="nfips,week")
## make the data weekly
udf <- sdf[, n := rank(date, ties.method="first"), by = key(sdf)][n == 1]
udf$start.full <- udf$pfull*as.numeric(floor(difftime(udf$start.first,min(sdf$date), units="weeks")))
udf <- subset(udf, !is.na(start.full))

```

## Start dates

```{r}
# start date not constant for 3 counties. Replace with min
# To see which 3:
## udf[,list(vs=var(start.full)),by=nfips][vs>0]
udf[, start.full:= ifelse(start.full>0, min(start.full), start.full), by=nfips]
# only one county with very early & late starts
udf[week==20,list(.N), by="start.full"][N<2, start.full]
udf[start.full>=23,start.full:=23]
udf[start.full>0 & start.full<=17,start.full:=17]

## Hybrid vs remote
udf$start.hybrid <- udf$phybrid*as.numeric(floor(difftime(udf$start.first,min(sdf$date), units="weeks")))
udf[, start.hybrid:= ifelse(start.hybrid>0, min(start.hybrid), start.hybrid), by=nfips]
#udf[week==20,list(.N), by="start.hybrid"]
```

# Event Studies

## School Visits, College Visits, Full-time Work behaviors, Stay-Home behavior, Gym/Church/Bar/Restaurant Visits

```{r}
## Incorrect DID event study
library(fixest)
reg <- feols(school ~ i(pfull, event_week, ref=-1)
             #+ i(phybrid, event_week, -1)
             #+ i(event_week, ref=-1)
             | fips + week, data=subset(udf, pfull | premote), cluster="fips")
foo <- coefplot(reg)
foo$prms$group <- ifelse(foo$prms$x<0, "pre", "post")
ggplot(data=foo$prms, aes(x=x, colour=group)) +
  geom_point(aes(y=y)) +
  geom_errorbar(aes(ymin=ci_low, ymax=ci_high)) +
  xlab("Weeks from school opening") +
  ylab("School Visits") +
    xlim(c(-6,14))  +
  ggtitle("Incorrect fixed effects regression comparing full school opening to remote school opening")


## Calloway Sant'Anna: Conditioning on group
# define a function that generates event-study figure
fun_event <- function(yname,gname,ylabel,df){
  out <- att_gt(yname=yname, gname=gname,
                idname="nfips",
                tname="week",
                xformla = ~1,
                #control="notyettreated",
                data=df,
                est_method="dr")
  es  <- aggte(out, type="dynamic")
  fig <- ggdid(es)  +
        labs(x = "Event Week", y = ylabel) + thm
  return(fig)
}

# define a wrapper function that generates four figures
fun_wrap <- function(yname,ylabel,yval,fname){
  # in-person remote
  fig <- fun_event(yname,"start.full",ylabel,subset(udf, (pfull | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of in-person remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_csfull.pdf",rootdir,fname), width=8, height=6)
  # in-person with no-mask vs remote
  fig <- fun_event(yname,"start.full",ylabel,subset(udf, (pfull_no | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of in-person with no-mask vs remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_csfullno.pdf",rootdir,fname), width=8, height=6)
  # hybrid vs remote
  fig <- fun_event(yname,"start.hybrid",ylabel,subset(udf, (phybrid | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of hybrid vs remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_cshybrid.pdf",rootdir,fname), width=8, height=6)
  # hybrid with no-mask vs remote
  fig <- fun_event(yname,"start.hybrid",ylabel,subset(udf, (phybrid_no | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of hybrid with no-mask vs remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_cshybridno.pdf",rootdir,fname), width=8, height=6)
}

### School Visits
fun_wrap(yname="school",ylabel="School Visits / Device",yval=c(-0.01,0.1),fname="school")

### College Visits
fun_wrap(yname="college",ylabel="College Visits / Device",yval=c(-0.01,0.023),fname="college")

### Full-time Work behavior
fun_wrap(yname="fullwork",ylabel="Full-time Work Visits / Device",yval=c(-0.004,0.035),fname="fullwork")

### Stay Home
fun_wrap(yname="home",ylabel="Stay Home / Device",yval=c(-0.04,0.06),fname="home")

### Restaurant Visits
fun_wrap(yname="restaurant",ylabel="Restaurant Visits / Device",yval=c(-0.04,0.045),fname="restaurant")

### Bar Visits
fun_wrap(yname="bar",ylabel="Bar Visits / Device",yval=c(-0.04,0.045),fname="bar")

### Gym Visits
fun_wrap(yname="gym",ylabel="Gym Visits / Device",yval=c(-0.01,0.01),fname="gym")

### Church Visits
fun_wrap(yname="church",ylabel="Church Visits / Device",yval=c(-0.01,0.01),fname="church")


```

## Cases, Deaths, log(Cases), log(Deaths)

```{r  cases-deaths}


## Incorrect DID event study
library(fixest)
reg <- feols(dcase_capita ~ i(pfull, event_week, ref=-1)
             #+ i(phybrid, event_week, -1)
             #+ i(event_week, ref=-1)
             | fips + week, data=subset(udf, pfull | premote), cluster="fips")
foo <- coefplot(reg)
foo$prms$group <- ifelse(foo$prms$x<0, "pre", "post")

ggplot(data=foo$prms, aes(x=x, colour=group)) +
  geom_point(aes(y=y)) +
  geom_errorbar(aes(ymin=ci_low, ymax=ci_high)) +
  xlab("Weeks from school opening") +
  ylab("Cases per 1000") +
    xlim(c(-6,14))  +
  ggtitle("Incorrect fixed effects regression comparing full school opening to remote school opening")


## Calloway Sant'Anna: Conditioning on group
# define a function that generates event-study figure
fun_event <- function(yname,gname,ylabel,df){
  out <- att_gt(yname=yname, gname=gname,
                idname="nfips",
                tname="week",
                xformla = ~1,
                control="notyettreated",
                data=df,
                est_method="dr")
  es  <- aggte(out, type="dynamic")
  fig <- ggdid(es)  +
        labs(x = "Event Week", y = ylabel) + thm
  return(fig)
}

# define a wrapper function that generates four figures
fun_wrap <- function(yname,ylabel,yval,fname){
  # in-person remote
  fig <- fun_event(yname,"start.full",ylabel,subset(udf, (pfull | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of in-person remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_csfull.pdf",rootdir,fname), width=8, height=6)
  # in-person with no-mask vs remote
  fig <- fun_event(yname,"start.full",ylabel,subset(udf, (pfull_no | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval)  +
      ggtitle("Event study of in-person with no-mask vs remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_csfullno.pdf",rootdir,fname), width=8, height=6)
  # hybrid vs remote
  fig <- fun_event(yname,"start.hybrid",ylabel,subset(udf, (phybrid | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of hybrid vs remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_cshybrid.pdf",rootdir,fname), width=8, height=6)
  # hybrid with no-mask vs remote
  fig <- fun_event(yname,"start.hybrid",ylabel,subset(udf, (phybrid_no | premote)))
  fig <- fig +  xlim(c(-6,14)) + ylim(yval) +
      ggtitle("Event study of hybrid with no-mask vs remote schooling")
  fig
  ggsave(sprintf("%s/tex/tables_and_figures/event_%s_cshybridno.pdf",rootdir,fname), width=8, height=6)
}

### New Cases
fun_wrap(yname="dcase_capita",ylabel="Weekly Cases / 1000",yval=c(-0.7,7),fname="cases")

### New Deaths
fun_wrap(yname="ddeath_capita",ylabel="Weekly Deaths / 1000",yval=c(-0.07,0.15),fname="deaths")

### log(Cases)
fun_wrap(yname="logdc",ylabel="log(Weekly Cases)",yval=c(-1.55,1.8),fname="logcases")

### log(Deaths)
fun_wrap(yname="logdd",ylabel="log(Weekly Deaths)",yval=c(-0.63,1.8),fname="logdeaths")


```



- [x] Make figures with hybrid & full. Levels and logs.

- [ ] Table summarizing data.

- [ ] Try restricting to K12 mask sample & look at college effect

- [x] Try to add hospitalization data

- [ ] Try Arellano-Bond and/or Anderson-Hsiao

- [ ] Look at correlation b/t level of cases & opening mode / date

- [ ] Discuss FE as $\beta_0$

- [ ] Summary statistics table: add differences in means (before/after opening) and clustered standard errors (see schoolopening.Rmd summary chunk)
      - also add post processing labels after

- [ ] C&S figures for other policies

- [ ] Find out about safegraph data policy

- [ ] Check policy discussion & message --- make sure it comes through
      clearly, so that journalists & public cannot misunderstand. Be
      sure that not to advocate school closing.
