---
title       : "Causal impact of masks, policies, behavior on early COVID-19 pandemic in the U.S."
subtitle    : "County Analysis"
author      :  Victor Chernozhukov, Hiro Kasahara, Paul Schrimpf
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        code_folding: hide
        self_contained : true
        fig_width: 8
        fig_height: 6
---

```{r setup, include=FALSE, cache=TRUE}
library(ggplot2)
library(data.table)
library(ggthemes)
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
source(paste(rootdir,"R/countyData.R",sep="/"))
source(paste(rootdir,"R/varlabels.R", sep="/"))
source(paste(rootdir,"R/dataprep.R",sep="/"))

covidCounty <- countyData(FALSE)
df <- dataprep(covidCounty)

startdate  <- "2020-01-01"
enddate <- as.Date(max(df$date,na.rm=TRUE))
class(enddate) <- "Date"
class(df$date) <- "Date"
sdf <- subset(df, as.Date(df$date)>=as.Date(startdate) & as.Date(df$date)<=enddate)

startdates <- c("start.Full in-person reopening available for all students",
                "start.Remote learning only",
                "start.Hybrid/Partial")
for (v in startdates) {
  sdf[,v] <- as.Date(sdf[,v])
}
enddates <- rep(NA, 3)
pvars <- c("full", "remote", "hybrid")
for(i in 1:length(startdates)) sdf[,pvars[i]] <-
                                 smoothedpolicy(sdf,startdates[i],enddatevar=enddates[i],type="ma",bw=1, id="fips")
haveschool=apply(sdf, 1, function(row) any(!is.na(row[startdates])))
portionnames  <- sub("start","portion",startdates[grep("start\\.",startdates)])
for (i in 1:length(pvars)) {
  sdf[,pvars[i]] <- sdf[,pvars[i]]*sdf[,portionnames[i]]
  sdf[!haveschool,pvars[i]] <- NA
}
```
# Safegraph Data

We process data from safegraph as follows:
- From the Weekly Patterns data, extract all POIs whose "top category" is one of:
    1. "Colleges, Universities, and Professional Schools",
    2. "Elementary and Secondary Schools",
    3. "Nursing Care Facilities (Skilled Nursing Facilities)",
    4. "Continuing Care Retirement Communities and Assisted Living Facilities for the Elderly"
    5. "Drinking Places (Alcoholic Beverages)"
    6. "Restaurants and Other Eating Places"
    7. "Fitness and Recreational Sports Centers"
    8. "Religious Organizations" (these are mostly churches)
- Extract daily device visits to each POI and aggregate visits to the county by category level
- Also extract weekly devices residing in each county from the Home Panel data
    - Note: the portion of all devices included in Safegraph varies
      over time and place. Safegraph recommends normalizing visits by
      devices residing to make changes comparable
      overtime. Normalizing by devices in county is what Safegraph calls the [macro normalization approach](https://docs.google.com/presentation/d/1a7lmVtulPpvuH-TPgsR_t5WUQPdT28c_ymyx_Bcankk/edit#slide=id.g86ef4ba4cf_0_874). There is a more detailed
      [micro normalization](https://colab.research.google.com/drive/16BELpcum4TKoH-5wg8Xym_CGgIGgpu1I?usp=sharing#scrollTo=B_dNARQFd50D)
      that looks at monthly
      visits to POI by the device's home census block group and normalize
      relative to devices residing in each census block group. If
      cross-county visits are rare or devices residing is highly
      correlated across counties, then normalizing by devices residing
      in the same county as a POI will give similar results.


## Figures

The following figures show devices residing and visits by category. Each black line is the evolution for a single county. Daily quantiles and means are shown by thicker colored lines. The y-axis is on a log-10 scale, but the mean is the mean of the level.

```{r rawcounts, cache=TRUE, echo=FALSE}
figtheme <- theme_hc
plotcountycounts <- function(var, datevar="date", groupvar="fips", df=data.table(sdf),
                             log10=TRUE) {
  if (!("data.table" %in% class(df))) {
    df <- data.table(df)
  }
  adf <- df[, list(mean = mean(get(var), na.rm=TRUE),
                   q5 = quantile(get(var), 0.05, na.rm=TRUE),
                   q50= quantile(get(var), 0.5, na.rm=TRUE),
                   q95= quantile(get(var), 0.95, na.rm=TRUE)),
            by=list(get(datevar))]
  fig <- ggplot(data=data.frame(df),aes_string(x=datevar)) +
    geom_line(aes_string(y=var, group=groupvar),alpha=0.1,colour="black") +
    geom_line(data=adf,aes(x=get, y=mean, color="mean"), size=2) +
    geom_line(data=adf,aes(x=get, y=q5, color="5%tile"), size=2) +
    geom_line(data=adf,aes(x=get, y=q50, color="50%tile"), size=2) +
    geom_line(data=adf,aes(x=get, y=q95, color="95%tile"), size=2) +
    scale_x_date(date_breaks = "months" , date_labels = "%b") +
    labs(color="") + xlab("") +
    figtheme()
  if (log10) {
    fig  <-  fig + scale_y_log10()
  }

  return(fig)
}

print(plotcountycounts("devices_residing") + ggtitle("Devices Residing"))
print(plotcountycounts("college_visits") + ggtitle("College/University Visits"))
print(plotcountycounts("school_visits") + ggtitle("K-12 Visits"))
print(plotcountycounts("nursing_visits") + ggtitle("Nursing Home Visits"))
print(plotcountycounts("assistedliving_visits") + ggtitle("Retirement Community Visits"))
print(plotcountycounts("church_visits") + ggtitle("Church Visits"))
print(plotcountycounts("bar_visits") + ggtitle("Bar Visits"))
print(plotcountycounts("restaurant_visits") + ggtitle("Restaurant Visits"))
print(plotcountycounts("gym_visits") + ggtitle("Gym Visits"))

```

The next four figures show visits to a category divided by devices
residing in a county.

```{r relfigs, cache=TRUE, echo=FALSE}
vars  <- c("college_visits","school_visits","nursing_visits","assistedliving_visits","gym_visits")
titles <- c("College/University","K-12","Nursing Home","Retirement Community","Gyms")
for (v in vars) {
  sdf[,sub("visits","rel",v)] <- sdf[,v]/sdf$devices_residing
  print(plotcountycounts(sub("visits","rel",v),log10=TRUE) + ggtitle(titles[vars==v]))
}
vars  <- c("college","school","bar","restaurant")
titles <- c("College/University","K-12 Schools","Bar Visits","Restaurants Visits")
for (v in vars) {
  print(plotcountycounts(v,log10=FALSE) + ggtitle(titles[vars==v]))
}

```


## Working

Safegraph reports the number of devices that are completely at home,
part-time working, and full-time working as part of their social
distancing metrics data. The part-time and full-time working device
counts are based on device location during daytime working hours. They
likely understate the portion of people working. See
[https://docs.safegraph.com/docs/social-distancing-metrics](https://docs.safegraph.com/docs/social-distancing-metrics)
for more information.

```{r working, cache=TRUE, echo=FALSE}
print(plotcountycounts("device_count", log10=FALSE) + ggtitle("Device Count"))
sdf$home_portion <- 100*sdf$completely_home_device_count/sdf$device_count
sdf$full_time_portion <- 100*sdf$full_time_work_behavior_devices/sdf$device_count
sdf$part_time_portion <- 100*sdf$part_time_work_behavior_devices/sdf$device_count
print(plotcountycounts("home_portion", log10=FALSE) + ggtitle("% completely home"))
print(plotcountycounts("full_time_portion", log10=FALSE) + ggtitle("% full-time work"))
print(plotcountycounts("part_time_portion", log10=FALSE) + ggtitle("% part-time work"))
```
